Verifying Spatial Properties of Stencil Computations

### 2016-11-15 paper.tex
5.3 space saving

We demonstrate the inference procedure over the
 program from Exmaple~\ref{exm:checking} (p.~\pageref{exm:checking})
 computing the mean of a five-point stencil:
%%
\begin{minted}{fortran}
do i = 1, (n-1)
  do j = 1, (m-1)
    x = a(i-1, j)+a(i+1, j); y = a(i, j-1)+a(i, j+1)
    b(i, j) = (a(i, j) + x + y) / 5.0
  end do
end do
\end{minted}
%
\subsubsection{Step 1: Standard analysis and data access analysis}
\label{sec:inf-step1}

The first step of the inference is to perform the
analysis of Section~\ref{subsec:analysis} to produce a
model of the code in terms of indexing schemes.
The \emph{analyse} and \emph{modelise} procedures before yielded the finite map:
%
\begin{align*}
\texttt{a} \mapsto \mathsf{only}(\{\vtwoh{-1}{0}, \vtwoh{1}{0},
          \vtwoh{0}{-1}, \vtwoh{0}{1}, \vtwoh{0}{0}\})
\end{align*}
%

>>>>

We illustrate each step of inference using the
 five-point stencil program from Example~\ref{exm:checking} (p.~\pageref{exm:checking}).

\subsubsection{Step 1: Data access analysis}
\label{sec:inf-step1}

The first step performs the
analysis of \S~\ref{subsec:analysis} to produce a
model of the code in terms of indexing schemes.
The \emph{analyse} and \emph{modelise} procedures before yielded the finite map:
%
\begin{align*}
\texttt{a} \mapsto \mathsf{only}(\{\vtwoh{-1}{0}, \vtwoh{1}{0},
          \vtwoh{0}{-1}, \vtwoh{0}{1}, \vtwoh{0}{0}\})
\end{align*}
%
